Assignment II\\Neural Networks and Deep Learning

### 2015-05-06 MLCV/ex2/report/report.tex
stylistic correction

	\title{Assignment II\\Neural Networks and Deep Learning}
	\author{Adam Kosiorek}	
	\markboth{Machine Learning for Applications in Computer Vision}{}
	\maketitle

@@

\section{Deriving Backpropagation}
    In his book, M.~Nielsen derived the Backpropgation algorithm for a sigmoid activation function $\sigma$ \cite{MLDL}. Here, following the notation, I derive it for an arbitrary function $f$.

@@

    \begin{equation}
    \begin{gathered}
      \delta^l = \frac{\partial C(a^L)}{\partial z^l} = \frac{\partial a^L}{\partial z^l} \nabla C(a^L) = \\ = \frac{\partial z^L}{\partial z^l} (f'(z^L) \odot \nabla C(a^L) ) = \frac{\partial z^L}{\partial z^l} \delta^L = \\ = diag(f'(z^l))(w^L)^T \delta^L = f'(z^L) \odot ((w^L)^T \delta^L)
    \end{gathered}
    \end{equation}

@@

    \begin{equation}
      \delta^l  = f'(z^{l+1}) \odot ((w^{l+1})^T \delta^{l+1})
    \end{equation}

    The final equations for gradients w.r.t. weights and biases do not depend on the activation function and has the same form as in \cite{MLDL}.

>>>>

	\title{Assignment II\\Neural Networks and Deep Learning}
	\author{Adam Kosiorek}	
	\markboth{Machine Learning for Applications in Computer Vision, Institute of Computer Vision, Technische Universit\'at M\"unchen}{}
	\maketitle

@@

\section{Deriving Backpropagation}
    In his book, M.~Nielsen derived the Backpropgation algorithm for the sigmoid activation function $\sigma$ \cite{MLDL}. Here, following the notation, I derive it for an arbitrary function $f$.

@@

    \begin{equation}
    \begin{gathered}
      \delta^l = \frac{\partial C(a^L)}{\partial z^l} = \frac{\partial a^L}{\partial z^l} \nabla C(a^L) = \\ = \frac{\partial z^L}{\partial z^l} (f'(z^L) \odot \nabla C(a^L) ) = \frac{\partial z^L}{\partial z^l} \delta^L = \\ = diag(f'(z^l))(w^L)^T \delta^L = f'(z^l) \odot ((w^L)^T \delta^L)
    \end{gathered}
    \end{equation}

@@

    \begin{equation}
      \delta^l  = f'(z^l) \odot ((w^{l+1})^T \delta^{l+1})
    \end{equation}

    The final equations for gradients w.r.t. weights and biases do not depend on the activation function and have the same form as in \cite{MLDL}.
